---
title: "Homework 1"
author: "Sophie Dalldorf"
date: "01/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

## Task 1

```{r mh_distance_function}
mh_distance <- function(x, y) {
  if (typeof(x) != typeof(y))
    {warning("x and y are not both logical, numeric, or character")
    return(-1)}
  if ((is.infinite(x) == TRUE) || (is.infinite(y) == TRUE) || 
      (is.nan(x) == TRUE) || (is.nan(y) == TRUE) ||
      (is.na(x) == TRUE) || (is.na(y) == TRUE))
    {warning("x or y take an Na, NaN, Inf, or -Inf")
    return(-1)}
  if ((nchar(x) != nchar(y)) & (typeof(x) != "logical"))
    {warning("x and y do not have the same number of digits or letters")
    return(-1)}
  if ((is.numeric(x) == TRUE) & (is.numeric(y) == TRUE))
    if ((x %% 1 != 0) || (y %% 1 != 0))
    {warning("x or y contains decimal values")
    return(-1)}
  if (typeof(x) == "character")
    {xasalist = strsplit(x, "")
    yasalist = strsplit(y, "")
    xasavector = unlist(xasalist)
    yasavector = unlist(yasalist)
    numtruefalse = xasavector != yasavector
    return(sum(numtruefalse, na.rm = TRUE))}
  if (typeof(x) == "double")
    {xchar = toString(x)
    ychar = toString(y)
    xasalist = strsplit(xchar, "")
    yasalist = strsplit(ychar, "")
    xasavector = unlist(xasalist)
    yasavector = unlist(yasalist)
    numtruefalse = xasavector != yasavector
    return(sum(numtruefalse, na.rm = TRUE))}
  if (typeof(x) == "logical")
    {if (((x == TRUE) & (y == TRUE)) || ((x == FALSE) & (y == FALSE)))
      {return (0)}
    return(1)}
}
```
    
## Task 2

**Initial test cases** (return a non-negative modified Hamming distance)

```{r test_cases}
mh_distance(x = "abc", y = "abc")
mh_distance(x = T, y = FALSE)
mh_distance(x = "523890", y = "752839")
mh_distance(x = 2341, y = 2350)
```

Added test cases that return a non-negative modified Hamming distance result.

```{r my_test_cases}
mh_distance(x = "trees", y = "bryss")
mh_distance(x = F, y = FALSE)
mh_distance(x = 3362863711, y = 3362863722)
mh_distance(x = "hi34two", y = "hey45w2")
mh_distance("goodbye", "GOODbye")
```

**Initial test cases** (return values of `-1`)

```{r bad_tests}
mh_distance(x = 52, y = 113)
mh_distance(x = "swimming", y = "winning")
mh_distance(x = NA, y = TRUE)
mh_distance(x = 1.5, y = 2.5)
```

Added test cases that return a value of `-1`.

```{r my_bad_tests}
mh_distance(x = 49765, y = 23)
mh_distance(x = Inf, y = "hellomynameissophie")
mh_distance("today", "yesterday")
mh_distance(x = TRUE, y = 23)
```

## Task 3

```{r vectorized_mh_distance_function}
vectorized_mh_distance <- function(a, b) {
  for (i in 1:length(a))
    if (nchar(a[i]) == nchar(b[i]))
      {print(paste0("The modified Hamming distance between ", a[i], " and ", 
                    b[i], " is ", mh_distance(a[i], b[i])))
    }
}
```

```{r vectorized_test}
s <- c(26, 50123, 456.12, 8, 0)
w <- c(22, 50000, 451.00, 88, 0)
vectorized_mh_distance(s, w)
```

## Task 4

Include a brief write-up that describes how you approached the problem 
and constructed your solution for Task 1.

For Task 1, I first wrote a for loop to go through each letter/number of the 
object, but in office hours, I learned that a for loop in this circumstance 
would be very inefficient. I switched my strategy to set the items equal to 
each other through a comparison operator, which gave me True and False outputs. 
I then realized that I could simply sum the number of True and False these to 
get the amount of letters/numbers that were the same for character and number 
objects. To handle invalid inputs, I wrote several if statements that would 
capture the invalid objects (e.g., if the type of x is not equal to the type of 
y) and return a warning. Initially, my statements did not do a great job; I got
errors because I would pass Inf or Nan into nchar, which are invalid inputs for 
that function. I simply had to switch around the order of the statements until 
I found one that did not give me errors. One of the weaknesses of my code is 
that it is pretty verbose. I use plenty of if statements and assign names to 
several values within my function, which makes it much longer than it needs to 
be and harder to find errors within 40 lines of code. Hopefully throughout the 
course I will learn how to be more concise in my coding.

