---
title: "Homework 1"
author: "Sophie Dalldorf"
date: "01/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

## Task 1
return exits the function
unlistgoes to a vector
```{r mh_distance_function}
mh_distance <- function(x, y) {
  if (typeof(x) != typeof(y))
    {warning("x and y are not both logical, numeric, or character")
    return(-1)}
  if ((is.infinite(x) == TRUE) || (is.infinite(y) == TRUE) || 
      (is.nan(x) == TRUE) || (is.nan(y) == TRUE) ||
      (is.na(x) == TRUE) || (is.na(y) == TRUE))
    {warning("x or y take an Na, NaN, Inf, or -Inf")
    return(-1)}
  if ((nchar(x) != nchar(y)) & (typeof(x) != "logical"))
    {warning("x and y do not have the same number of digits or letters")
    return(-1)}
  if ((is.numeric(x) == TRUE) & (is.numeric(y) == TRUE))
    if ((x %% 1 != 0) || (y %% 1 != 0))
    {warning("x or y contains decimal values")
    return(-1)}
  if (typeof(x) == "character")
    {xasalist = strsplit(x, "")
    yasalist = strsplit(y, "")
    xasavector = unlist(xasalist)
    yasavector = unlist(yasalist)
    numtruefalse = xasavector != yasavector
    return(sum(numtruefalse, na.rm = TRUE))}
  if (typeof(x) == "double")
    {xchar = toString(x)
    ychar = toString(y)
    xasalist = strsplit(xchar, "")
    yasalist = strsplit(ychar, "")
    xasavector = unlist(xasalist)
    yasavector = unlist(yasalist)
    numtruefalse = xasavector != yasavector
    return(sum(numtruefalse, na.rm = TRUE))}
  if (typeof(x) == "logical")
    {if ((x & y == TRUE) || (x & y == FALSE))
      {return (0)}
    return(1)}
}
```
    
  
## Task 2

<i>
Be sure to remove chunk option `eval=FALSE` in the below code chunks
once you create `mh_distance()`. Do not include this italicized
text in your final submission.
</i>

**Initial test cases** (return a non-negative modified Hamming distance)

```{r eval=FALSE}

mh_distance(x = "abc", y = "abc")
mh_distance(x = T, y = FALSE)
mh_distance(x = "523890", y = "752839")
mh_distance(x = 2341, y = 2350)
```

Added test cases that return a non-negative modified Hamming distance result.

```{r}
mh_distance(x = "trees", y = "bryss")
mh_distance(x = F, y = FALSE)
mh_distance(x = 3362863711, y = 3362863722)
mh_distance(x = "hi34two", y = "hey45w2")
```

**Initial test cases** (return values of `-1`)

```{r eval=FALSE}
mh_distance(x = 52, y = 113)
mh_distance(x = "swimming", y = "winning")
mh_distance(x = NA, y = TRUE)
mh_distance(x = 1.5, y = 2.5)
```

Added test cases that return a value of `-1`.

```{r}
mh_distance(x = 49765, y = 23)
mh_distance(x = Inf, y = "hellomynameissophie")
mh_distance("today", "yesterday")
mh_distance(x = TRUE, y = 23)
```


## Task 3

Consider the pair of vectors `s` and `w` given below.


Function mh_distance() is not vectorized. Write a loop to compute the modified Hamming distance for the pair of vectors given in the R Markdown file. For those element pairs that have a valid modified Hamming distance (not -1), a statement should be printed stating the distance for the given pair. An example is given below.

```{r}
vectorized_mh_distance <- function(a, b) {
  for (i in 1:length(a))
    if (nchar(a[i]) == nchar(b[i]))
#      {moddist = mh_distance(a[i], b[i])
      {print(paste0("The modified Hamming distance between ", a[i], " and ", b[i], " is ", mh_distance(a[i], b[i])))
    }
}
```


```{r}
s <- c(26, 50123, 456.12, 8, 0)
w <- c(22, 50000, 451.00, 88, 0)
vectorized_mh_distance(s, w)
```

## Task 4


